On Determinism of Game Engines used for Simulation-based Autonomous Vehicle Verification

### 2021-04-09 paper/cav_determinisim_main.tex
greg and kevin bios added

>>>>

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{Other/mugs/greg.png}}]{Greg Chance}
Greg Chance received the B.Sc. (Hons.) and Ph.D. degrees in physics from the University of Bath, Bath, U.K., in 2001 and 2005, respectively. He was previously at the Bristol Robotics Lab and is currently a Senior Research Associate with the Trustworthy Systems Laboratory, University of Bristol, Bristol, U.K. His current research interests are simulation-based verification for autonomous systems and cybersecurity. He has ten years industrial experience researching for Oxford Instruments, U.K., and BAE Systems, U.K. Dr Chance is a Chartered Engineer and a member of the Institute of Physics and holds a patent for a novel plasma control method. 
\end{IEEEbiography}

\begin{IEEEbiography}{Abanoub Ghobrial}
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{Other/mugs/kevin.jpg}}]{Kevin McAreavey}
Kevin McAreavey received a BSc (Hons) in computer science from Queen's University Belfast (QUB) in 2010 followed by a PhD in AI in 2014. He is currently a Senior Research Associate with the Intelligent Systems Laboratory at the University of Bristol (UOB), working on explainable AI for AI-enabled domestic life. Previously he has worked with the Trustworthy Systems Laboratory at UOB and as a Research Fellow at QUB. His research interests are broadly in the areas of knowledge representation and reasoning, agents and multi-agent systems, and automated planning.
\end{IEEEbiography}

\begin{IEEEbiography}{Severin Lemaignan}
\end{IEEEbiography}

\begin{IEEEbiography}{Tony Pipe}
\end{IEEEbiography}

\begin{IEEEbiography}{Kerstin Eder}
\end{IEEEbiography}
